An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-19 paper/paper.tex
Final changes from Tom

The current self-imposed deadline for HTTP/2.0 is July
2013~\cite{httpbis-charter}.  So far, three likely starting points for
the specification have been proposed: Google's SPDY, Microsoft's Speed +
Mobility, and a "Network-Friendly" proposal from a handful of Open Source
authors. The three will be briefly outlined beginning in
\S\ref{sec:background/spdy} and then the remainder of the paper will focus on
measurements of the most viable candidate for HTTP/2.0, SPDY.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Speed+Mobility}
\label{sec:background/s+m}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This proposal~\cite{sm} comes from Microsoft.  It shares much in common with
SPDY, but with a few major differences. First is that rather than defining
their own session layer, Microsoft S+M relies on WebSockets for a session
layer.  In addition, S+M uses an HTTP header to negotiate the protocol upgrade
rather than SPDY's use of the SSL/TLS handshake to do this same thing. This
adds another round trip after the connection is established, and requires the
endpoint to analyze the HTTP headers. This is friendly to intermediate proxies
that do not support S+M, but it quite a bit of latency to beginning the actual
communication and is one of the reasons that Facebook endorsed SPDY over
S+M~\cite{fbook}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
\label{sec:research/overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This project sets out to answer that question in two fashions. First, we will
perform an in-depth examination of what is the limiting factor of current
HTTP/1.1 including a review of literature in the area and a characterization of
real-world web page asset size distribution in \S\ref{sec:assets} (and
how we predict the same assets will load if loaded over SPDY). Since SPDY can
combine asset requests into a single multiplexed TCP connection, we identify
this as a significant source of performance improvement over HTTP. We will
perform this by collecting the assets from the top Alexa sites with the Web
Asset Scraper described in \S\ref{sec:research/scraper}.

@@

@@

Figure \ref{fig:combination-ssl-and-ip} shows that, in the common-to-worst
case, 90\% of sites will halve the number of connections by switching to SPDY
and 40\% could load using one-fifth the connections.

>>>>

The current self-imposed deadline for HTTP/2.0 is July
2013~\cite{httpbis-charter}.  So far, three likely starting points for
the specification have been proposed: Google's SPDY, Microsoft's Speed +
Mobility, and a ``Network-Friendly'' proposal from a handful of Open Source
authors. The three will be briefly outlined beginning in
\S\ref{sec:background/spdy} and then the remainder of the paper will focus on
measurements of the most viable candidate for HTTP/2.0, SPDY.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Speed+Mobility}
\label{sec:background/s+m}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This proposal~\cite{sm} comes from Microsoft.  It shares much in common with
SPDY, but with a few major differences. First is that rather than defining
their own session layer, Microsoft S+M relies on WebSockets for a session
layer.  In addition, S+M uses an HTTP header to negotiate the protocol upgrade
rather than SPDY's use of the SSL/TLS handshake to do this same thing. This
adds another round trip after the connection is established, and requires the
endpoint to analyze the HTTP headers. This is friendly to intermediate proxies
that do not support S+M, but it adds additional latency (1 RTT) to beginning
the actual communication and is one of the reasons that Facebook endorsed SPDY
over S+M~\cite{fbook}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
\label{sec:research/overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This project sets out to answer that question in two fashions. First, we will
perform an in-depth examination of what is the limiting factor of current
HTTP/1.1 including a characterization of real-world web page asset size
distribution in \S\ref{sec:assets} and how we predict the same assets will load
if loaded over SPDY. Since SPDY can combine asset requests into a single
multiplexed TCP connection, we identify this as a significant source of
performance improvement over HTTP. We will perform this by collecting the
assets from the top Alexa sites with the Web Asset Scraper described in
\S\ref{sec:research/scraper}.

@@

From this data, we analyzed the theoretical benefit of asset combination for SPDY in Section \ref{sec:assets}.

@@

Figure \ref{fig:combination-ssl-and-ip} shows that, in the common-to-worst
case, 90\% of sites will halve the number of connections by switching to SPDY
and 40\% could load using one-fifth the connections while only about 7\% see no
improvement with SPDY.
